---
title: "Analysis of Variance"
author: "LoveA"
date: '2022-07-25'
output: html_document
---

                  Analysis Of Variance using R

Anova is the analysis of comparing averages of three or more population

data: gapminder

data location: R-studio

load libraries
```{r}
library(tidyverse)
library(gapminder)
library(patchwork)
library(forcats)
```

Population sample: "Asia", "Americas", "Europe"

Research Question: Is the life expectancy in these three countries different?

Hypotheses Testing:

* H0: There's no difference in the mean life expectancy in the three                           population, Mean life expectancy is the same.

* H1: Mean life expectancy is not the same.

Observation: Difference in mean is observed in the sample data,but is this statistically significant (alpha = 0.05)

Let's create a new dataset from gapminder
```{r}
data <- gapminder %>% 
  filter(continent %in% c("Asia", "Americas", "Europe"),
         year == 2007) %>% 
  select(continent, lifeExp)
```

Now we have created a new dataset, let's analyse the distribution of mean 

```{r}
data %>% 
  group_by(continent) %>% 
  summarise(mean = mean(lifeExp)) %>% 
  arrange(mean)
```

Now we have seen the distribution of mean.

Let's create ANOVA Model
```{r}
data %>% 
  aov(lifeExp ~ continent, data =.) %>% 
  summary()
```
P-value is less than 5%, it indicate there's significant difference in the mean lifeExp of the three population.

H0: Is Rejected
H1: Is Accepted

Note: How to know which population is actually different from each other.

```{r}
data %>% 
  aov(lifeExp ~ continent, data =.) %>% 
  TukeyHSD()
  
```

The result states that Europe - Asia has a large significant difference having a p-value of 1.89e-05










