---
title: "simple data visualization"
author: "LoveA"
date: '2022-07-25'
output: html_document
---

                           My First Data Visualization 

let's load some libraries
```{r}
library(tidyverse) # helps us to interact with data
library(gapminder) # Gives us access to the dataset "gapminder"
library(patchwork) # Helps in data visualization
```

```{r}
data() # shows data stored in R
```
data: gapminder

* Question 1: What is the mean life expectancy in "Africa" ?
```{r}
View(gapminder) # to view the data set
```
N/B:   we will be using %>% operator and some functions in our coding

* %>% => This is called 'piped in operator'. It informs R about the data you want to bring into the next line of code.

```{r}
gapminder %>% 
  filter(continent =="Africa") %>%  # used to filter out the particular population 
  select(lifeExp, continent) %>%    # select() used to select the variable
  summarise(mean = mean(lifeExp))   # summarise() used to summarise result
```
Answer: The mean life expectancy in Africa is 48.9yrs

The mean life expectancy can also be calculated using Pull()
```{r}
gapminder %>% 
  filter(continent =="Africa") %>% 
  pull(lifeExp) %>% 
  mean() %>% 
  signif(4)     # helps to round up to 4 decimal point

```

Data Visualization: Plot a density graph for the mean life Expectancy in Africa

before we include ggplot to our code, let's assing the value of the mean life expectancy in Africa to a variable. that variable will be called "mean_x"

```{r}
mean_x <- gapminder %>% 
  filter(continent =="Africa") %>% 
  pull(lifeExp) %>% 
  mean() %>% 
  signif(4)
```

```{r}
View(mean_x) # view the variable
```
 
```{r}
gapminder %>% 
  filter(continent =="Africa") %>% 
  select(continent,lifeExp) %>% 
  ggplot(aes(lifeExp))+
  geom_density(fill="blue", alpha = 0.5)+
  scale_x_log10()+
  geom_vline(xintercept = mean_x, color="red")+
  labs(title = "Mean lifeExp in Africa")+
  annotate("text", x=60, y=4.5, label ="mean lifeExp is 48.87")
```
 
* Question 2: calculate the mean life expectancy for all continent and plot a    graph indicating point of each variances.

First of all; let's calculate the mean lifeExp for the five continent

```{r}
 gapminder %>% 
  select(continent, lifeExp) %>% 
  group_by(continent) %>% 
  summarise(mean =mean(lifeExp)) %>%
  arrange(mean)
```
Answer: Africa 48.9; Asia 60.1; Americas 64.7; Europe 71.9; Oceania 74.3

Now, let's create a new object called "p" and assign the mean values to it
```{r}
p <- gapminder %>% 
  select(continent, lifeExp) %>% 
  group_by(continent) %>% 
  summarise(mean =mean(lifeExp)) %>%
  arrange(mean)
```
Let's include ggplot to our code
```{r}
p %>% 
  ggplot(aes(x=mean, y= continent))+
  geom_point(size =1, color="red")+
  labs(title = "A plot showing mean lifeExp for each continent",
       x = "mean_lifeEXP")
```


